---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Lucy Lithgow"
output: 
  html_document:
    theme: cerulean
    highlight: haddock
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse)
```

<br><br>

## Introduction

[Fast food calories dataset](https://github.com/rfordatascience/tidytuesday/blob/master/data/2018/2018-09-04/fastfood_calories.csv):
The fast food dataset includes 8 unique fast food restaurants and information on their menu items including calories, sodium, fat, sugar, protein and more. I selected this dataset because it has a lot of information to work with and it will be interesting to compare the nutrition facts from different popular fast food chains, or compare the menu items from within the same restaurant.

```{r read-examine-data}
fastfood <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')

glimpse(fastfood)
```

<br><br>

## Question 1

#### Which fast food restaurant has the highest average calories per menu item?

### Methods
```{r question 1 histogram}
fastfood %>%
  group_by(restaurant) %>% #add grouping
  summarise(mean_calories = mean(calories)) %>% #find mean calories per restaurant
  ggplot() +
  aes(x = restaurant, #restaurant on x axis
      y = mean_calories, #mean calories on y axis
      fill = restaurant) + #map restaurant to fill
  geom_col() + #histogram
  geom_text(aes(label = round(mean_calories, digits = 2), #label each mean calories and round
                y = mean_calories +20), check_overlap = T) + #move label and remove overlap
  theme_bw() + #set theme
  labs(x = "Restaurant",
       y = "Average calories") + #rename axis
  scale_color_brewer() + #set color theme
  theme(legend.position = "none") #remove legend

```

### Answer

The McDonald's menu contains the items with the highest average calories.


<br><br>

## Question 2

#### Which fast food signature sandwhich is highest in calories?

### Methods
```{r question 2 lollipop}
fastfood %>%
  filter(item %in% c("Big Mac", "Chicken Sandwich", "Sonic Cheeseburger W/ Ketchup", "Classic Roast Beef", "WHOPPER w/ Cheese", "Original Cheeseburger")) %>% #filter to choose signature sandwiches
  ggplot() +
  aes (x = reorder(restaurant, -calories), #set x and y axis, order descending
       y = calories) +
  geom_point(color = "deeppink") + #add just a color to point
  geom_segment(color = "deeppink", #add just a color to line
    aes(x = restaurant,
               y = 0,
               xend = restaurant,
               yend = calories)) + #tell lollipop where to start and end
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) + #fix labels to remove overlap
  scale_color_brewer() + #set color scheme
  geom_text( size = 3,
    aes(label = item,
            y = calories + 40)) + #label mean values
  theme_light() + #set theme
  labs(x = "Restaurant",
       y = "Calories") #rename axis titles
  
```

### Answer

The Whopper with cheese from Burger King is highest in calories compared to other fast food restaurant's signature sandwiches. 

<br><br>

## Question 3

#### Which restaurant has the lowest average trans fat per menu item?

### Methods
```{r question 3 histogram}
fastfood %>%
  group_by(restaurant) %>%
  summarise(mean_transfat = mean(trans_fat)) %>%
  ggplot() +
  aes(x = reorder(restaurant, -mean_transfat),
      y = mean_transfat,
      fill = restaurant) +
  geom_col() +
  geom_text(aes(label = round(mean_transfat, digits = 2),
                y = mean_transfat + .03)) +
  theme_bw() +
  labs(x = "Restaurant",
       y = "Average trans fats") +
  scale_color_brewer() +
  theme(legend.position = "none")


```

### Answer

Chick Fil-A's menu items on average have the lowest trans fats.


<br><br>

## Question 4

#### Which restaurant's chicken menu items are a better source of protein, Mcdonald's or Chick Fil-A?

### Methods
```{r question 4 violin}
fastfood %>%
  filter(restaurant %in% c("Mcdonalds", "Chick Fil-A")) -> restaurants

restaurants %>%
  filter(X1 %in% c(1,4,5, 8, 13, 14, 18, 19, 20, 24, 25, 26, 27, 30, 31, 33:82)) -> justchicken

justchicken %>%
  ggplot() +
  aes(x = restaurant,
      y = protein,
      fill = restaurant) +
  geom_violin() +
  scale_fill_manual(values = alpha(c("blue", "gold"), .3)) +
  stat_summary(fun = mean, geom ="point", shape=23, size=3) +
  theme_linedraw() +
  labs(x = "Restaurant",
       y = "Protein") +
  theme(legend.position = "none")

```

### Answer

The average protein value for chicken based menu items is higher at Mcdonald's compared to Chick Fil-A.
